The Role of Advection Versus Diffusion in Intraventricular Transport

### 2025-02-24 paper/main.tex
minor fix

\subsection{Discretization of the advection-diffusion equation}
We outline the discretization of the advection-diffusion weak formulation
for the baseline model, defined
by~\Cref{eq:adv_diff_weak_formB,eq:adv_diff_skew_form,eq:adv_diff_linear_form}.
The weak formulation is discretized with a symmetric interior-penalty method using
discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}.
Let the subscript $h$ denote discrete variables. Exchanging the
variables in~\Cref{eq:adv_diff_weak_formB} with their discrete
counterparts yields the discrete weak form: find $c_h\in W_h$ such that
\begin{equation*}
    a(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h), \quad\forall\phi_h\in W_h.
\end{equation*}
The space $W_h$ is constructed with finite elements with
discontinuous Lagrange polynomial basis functions:
\begin{equation}
    W_h = \Big\{w_h : w_h\in L^2;  w_h\vert_K\in P_k; \forall K\in\Omega_h\Big\}.
\end{equation}
These elements allow for discontinuities in the discrete solution across element edges.
To ensure a stable discretization with these elements, we add the stabilization
\begin{equation}
    \begin{aligned}
        a_{\mathrm{stab}}(c_h, \phi_h)
        = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
        +\sum_{f\in \mathcal{F}}\int_f{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
         -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
         -\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
    \end{aligned}\label{eq:SIP_stabilization}
\end{equation}
to the discrete weak formulation, where
\begin{equation*}
    \hat{u}_h = \frac{1}{2}\left(\uu_h\cdot\nn + \vert\uu_h\cdot\nn\vert\right)
\end{equation*}
is used to upwind the velocity $\uu_h$, with the velocity upwinded with respect to a
facet $\mathcal{F}_k$. The stabilization parameter $\alpha>0$ must be chosen
large enough to achieve stability. The average and jump operators used
in~\Cref{eq:SIP_stabilization} are defined, respectively, as
\begin{equation*}
    \avg{c} = \frac{c^+ + c^-}{2} \qquad\mathrm{and}\qquad \jump{c} = c^+\nn^+ + c^-\nn^-.
\end{equation*}
The final discrete weak formulation of the advection-diffusion equation is:
find $c_h\in W_h$, such that
\begin{equation}
    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h),
    \quad\forall\phi_h\in W_h.
    \label{eq:discrete_weak_form_adv_diff}
\end{equation}
In this work, we solved~\Cref{eq:discrete_weak_form_adv_diff} numerically
with the penalty parameter value $\alpha=25$.

@@

Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s.
The maximum mean velocities
in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for
$\overline{u}_x$ and $\overline{u}_y$,
respectively. We used the only-cardiac/no-cilia flow model to tune the
pressure boundary condition
amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a
maximum velocity magnitude
of 4.8 \textmu m/s, which is close to the maximum observed in the
particle tracking data when
rejecting the outlier at around 10 \textmu m/s; (ii) it yields a time-averaged mean velocity
of 0.89 \textmu m/s, which is close to the mean observed in the particle tracking data.
\begin{figure}[H]
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
    \end{minipage}
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
    \end{minipage} 
    \caption{Particle tracking data. Mean velocities in
    the $x$ (\textbf{a.}) and $y$ (\textbf{b.}) directions of the particles tracked.
    The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
\end{figure}

>>>>

\subsection{Discretization of the advection-diffusion equation}
We outline the discretization of the advection-diffusion weak formulation
for the baseline model, defined
by~\Cref{eq:adv_diff_weak_formB,eq:adv_diff_skew_form,eq:adv_diff_linear_form}.
The weak formulation is discretized with a symmetric interior-penalty method using
discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}.
Let the subscript $h$ denote discrete variables. Exchanging the
variables in~\Cref{eq:adv_diff_weak_formB} with their discrete
counterparts yields the discrete weak form: find $c_h\in W_h$ such that
\begin{equation*}
    a(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h), \quad\forall\phi_h\in W_h.
\end{equation*}
The space $W_h$ is constructed with finite elements with
discontinuous Lagrange polynomial basis functions:
\begin{equation}
    W_h = \Big\{w_h : w_h\in L^2;  w_h\vert_K\in P_k; \forall K\in\Omega_h\Big\}.
\end{equation}
These elements allow for discontinuities in the discrete solution across element edges.
To ensure a stable discretization with these elements, we add the stabilization
\begin{equation}
    \begin{aligned}
        a_{\mathrm{stab}}(c_h, \phi_h)
        = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
        +\sum_{f\in \mathcal{F}}\int_f{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
         -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
         -\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
    \end{aligned}\label{eq:SIP_stabilization}
\end{equation}
to the discrete weak formulation, where
\begin{equation*}
    \hat{u}_h = \frac{1}{2}\left(\uu_h\cdot\nn + \vert\uu_h\cdot\nn\vert\right)
\end{equation*}
is used to upwind the velocity $\uu_h$ with respect to a
facet. The stabilization parameter $\alpha>0$ must be chosen
large enough to achieve stability. The average and jump operators used
in~\Cref{eq:SIP_stabilization} are defined, respectively, as
\begin{equation*}
    \avg{c} = \frac{c^+ + c^-}{2} \qquad\mathrm{and}\qquad \jump{c} = c^+\nn^+ + c^-\nn^-.
\end{equation*}
The final discrete weak formulation of the advection-diffusion equation is:
find $c_h\in W_h$, such that
\begin{equation}
    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h),
    \quad\forall\phi_h\in W_h.
    \label{eq:discrete_weak_form_adv_diff}
\end{equation}
In this work, we solved~\Cref{eq:discrete_weak_form_adv_diff} numerically
with the penalty parameter value $\alpha=25$.

@@

Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s.
The maximum mean velocities
in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for
$\overline{u}_x$ and $\overline{u}_y$,
respectively. We used the only-cardiac/no-cilia flow model to tune the
pressure boundary condition
amplitude $A$. The choice of $A=1.5$ mPa was used since: (i) it yields a
maximum velocity magnitude
of 4.8 \textmu m/s, which is close to the maximum observed in the
particle tracking data when
rejecting the outlier at around 10 \textmu m/s; (ii) it yields a time-averaged mean velocity
of 0.89 \textmu m/s, which is close to the mean observed in the particle tracking data.
\begin{figure}[H]
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
    \end{minipage}
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
    \end{minipage} 
    \caption{Particle tracking data. Mean velocities in
    the $x$ (\textbf{a.}) and $y$ (\textbf{b.}) directions of the particles tracked.
    The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
\end{figure}
